\chapter{Results and Insights}

There were are some promising insights gained over the course of the project.
Table~\ref{tab:results} indicates the difference in uniqueness for various browser characteristics when no fingerprinting defenses are enabled compared to when the add-on and recommended settings are enabled.
A larger percentage indicates a more common value for a particular characteristic.
The presented figures are calculated using \url{browserprint.info}, which provides how common each fingerprint characteristic is relative to all other users that have retrieved their fingerprint using the service.
A Sony Vaio laptop with the OpenSuse Linux distribution was used for testing, running Firefox as the browser of choice.

With the add-on and recommended settings, both \url{panopticlick.eff.org} and \url{browserprint.info} found the test browser's fingerprint to be a unique one.
Panopticlick states how many bits of identifying information each characteristic exposes, adding up to a total of 63.75 bits for the test computer when the add-on was not used.
This is calculated with $\log_{2}x$, where $x$ is the total number of fingerprints taken divided by the number of fingerprints that share this value (including the new fingerprint).
This total also does not include the User Agent (as there is an overlap between the information provided by the User Agent and other properties such as the platform) and excludes Flash fingerprinting information.
When the add-on and font whitelist are enabled, the bits of identifying information drops to 50.24 bits.
This is not a bad result when considering that an increase of one bit doubles the amount of information exposed as the increase is exponential.
However, this is still very far above the minimum number of bits required to uniquely map Panopticlick's sample size.
For their 233,722 fingerprints they had retrieved at the time of this test (3 May 2017), assuming every fingerprint is unique, they only require 17.834 bits of identifying information from every browser ($\log_{2}233722$).
The chance of these browsers all being unique is small, so it is likely that the practical number of bits required is higher than this, though research is needed to determine an estimate of how many bits of identifying information are needed in a real-world application of fingerprinting.
The remainder of this chapter will discuss the various parts of the browser that expose information, the methods used to try to restrict them and how successful they were.

\begin{table}[h!]
\centering
\begin{tabular}{| p{6cm} | p{4cm} | p{4cm} |}
    \hline
    \textbf{Browser Characteristic} & \textbf{Frequency of value without add-on and settings} & \textbf{Frequency of value with add-on and settings} \\ \hline
    \texttt{Platform (Flash)} & {0.015\%} & {38.46\%} \\ \hline
    \texttt{Screen Size (Flash)} & {10.5\%} & {38.46\%} \\ \hline
    \texttt{Language (Flash)} & {25.38\%} & {38.46\%} \\ \hline
    \texttt{System Fonts (Flash)} & {0.022\%} & {38.46\%} \\ \hline
    \texttt{Plugins} & {0.621\%} & {0.056\%} \\ \hline
    \texttt{System Fonts (JavaScript)} & {0.08\%} & {0.03\%} \\ \hline
    \texttt{Canvas Fingerprint} & {0.068\%} & {2.729\%} \\
    \hline
\end{tabular}
\caption{Frequency of browser characteristics without protection vs.\ with protection (retrieved from \url{browserprint.info})}
\label{tab:results}
\end{table}

\section{HTTP Request Headers}

Although in an early stage of development, a few of the HTTP request headers were edited, after further research it was clear that it was not effective for more complex fingerprinters.
The spoofing of the User Agent does not work because fingerprinters are able to query various JavaScript functions and objects available across different browsers and through process of elimination deduce what browser, browser version and platform are being used.
An example of this is querying for the \texttt{ActiveXObject} in the \texttt{window} object, which is available only on the Internet Explorer web browser \citep{activeX}.
The only defence against this is to disable JavaScript altogether.
Unfortunately, this has a big impact on usability due to approximately 94.5\% of all websites use JavaScript \citep{w3-javascript}.
The other headers that could be altered are the HTTP\_ACCEPT headers, particularly the language header, and the date header.
Once again changing these have consequences for the usability of many websites.

\section{Navigator Properties}

Similarly to the HTTP request headers, many of the \texttt{window.navigator} properties can be inferred using JavaScript such as \texttt{appName}, \texttt{appVersion}, \texttt{platform}.
Due to this, these \texttt{navigator} properties are not spoofed in the final version of the add-on.
After much investigation, it does not seem possible to convincingly disguise a browser as a different browser due to the significant number of differences between every browser API as well as there being a number of values and functions that can not be spoofed, such as the floating point difference in math functions discussed in Chapter 3.
Though simple fingerprinters may be tricked easily, due to the dynamic nature of web security, simpler tricks such as spoofing \texttt{navigator} properties can not be expected to work for very long before websites improve the fingerprinting scripts they use, once again making it more difficult to mitigate.

The only \texttt{navigator} property that seems promising to spoof is the \texttt{plugins} property.
The add-on successfully hides all installed plugins apart from Flash due to it being set to `click-to-play', however on \url{browserprint.info}'s fingerprint checker, hiding the plugins installed on the test computer greatly increased how unique the browser was.
The percentage of users with the same plugins decreased from 0.621\% to 0.056\%, clearly a diminished figure that makes the fingerprint more unique.
Although this is not an entirely positive result, it does show promise as the list of plugins could potentially be spoofed to return some of the most commonly installed plugins.
More research is required to determine what these commonly installed plugins are across different browsers and browser versions, as this was too large an undertaking for the scope of the project.

\section{Font Fingerprinting}

Changing the whitelist of system fonts was an easy method of changing what system fonts fingerprinters detect.
However, it was difficult to ascertain a set of fonts that reduced the browser's uniqueness score as the information for what fonts are most common for different operating systems is not readily available, and similarly to the list of plugins, would require a significant amount of further research.
After changing the whitelist to contain a subset of the fonts that could be gleamed by the fingerprinter through JavaScript, the percentage of users with the same set of fonts decreased from 0.08\% to 0.03\%.
After experimenting with this for some time it was clear that the solution was not one that could be reached easily through trial and error.

There is potential for the add-on to developed further and to use randomisation solely for the font list as it is one of the biggest sources of entropy in a browser fingerprint, and is a characteristic that one would not expect to have significant changes very often.
The ease of altering the whitelist is hugely beneficial to mitigating fingerprinting, and is a good sign that browser developers are beginning to take steps towards combatting fingerprinting.

\section{Flash}

As shown in Table~\ref{tab:results}, disabling Flash yielded a huge decrease in uniqueness for the browser.
It is important to note that the characteristics were not all orthogonal to others gained by fingerprinting.
For example, the browser's platform can also be gained through the \texttt{window.navigator}, albeit with less information.
It is still clear to see that Flash is one of the most important (and simplest) steps to mitigating fingerprinting, usability issues aside.

\section{Canvas Fingerprinting}

Blocking canvas fingerprinting resulted in a value for the fingerprint that was roughly 4,000\% more common than when a canvas fingerprint could be retrieved.
This seems like a huge improvement in how common the browser appears, though it is very difficult to determine if this value being shared with roughly 2.7\% of other browsers is enough of an improvement to make a significant difference in the uniqueness of the fingerprint as a whole.
To answer this, one would require access to a broad sample of user data to know for sure just how significant an improvement this is.
The \url{browserprint.info} fingerprinting test has a sample size of roughly 32,000 users \citep{browserprint}, many of whom can be assumed to be somewhat privacy aware.
One can assume that the 2.7\% figure would be inflated on \url{browserprint.info} when compared to fingerprints retrieved from an average website, when considering that with a higher proportion of privacy aware users, there would be a higher proportion of users that would have JavaScript disabled.
For these users, the fingerprinter would not be able to retrieve a canvas fingerprint.
Viewed in isolation, the decrease in uniqueness with the canvas fingerpringing defence is a good result, but once again the question of `Is it enough of an improvement to make a difference?', is asked and the answer is not at all obvious.

